---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# perumapas

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
[![CRAN status](https://www.r-pkg.org/badges/version/perumapas)](https://CRAN.R-project.org/package=perumapas)
<!-- badges: end -->

The goal of `perumapas` is to have an easy way to draw maps with peruvian shapes.

## Installation

You can install the released version of perumapas from the [calderonsamuel r-universe](https://calderonsamuel.r-universe.dev/) with:

``` r
install.packages("perumapas", repos = 'https://calderonsamuel.r-universe.dev')
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r}
library(perumapas)
library(ggplot2) # for plotting
library(dplyr) # for filtering
library(sf) # obligatorio!
```

You can create maps easily.


```{r example}
mapa_distrital %>% 
  filter(departamento == "LIMA", provincia == "LIMA") %>% 
  ggplot() +
  geom_sf()
```

You have the *ubigeo* field to easily join/merge with another dataset.

```{r}
head(mapa_distrital, 10)
```

To learn how to use `mapa_regional` and `mapa_provincial` see `vignette('basic-usage')`.
